### 2019-06-04 doc/chapters/trying_verify_checktx.tex
added some labels
consistend titles
moved image
changed sentence

\chapter{Trying to Verify checkTransaction}
\label{chap:connecting}

@@

\section{Process of the Verification // TODO change?}

@@

The extracted code has more than 1500 lines.
After running Stainless on it, it throws a really huge bunch of errors about what Stainless can not reason about.
This would require to change nearly all the extracted code.

@@

@@

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.5]{images/bitcoin-s-pr-comment.png}
	\caption{Nice catch comment on PR \#435 from GitHub}
	\label{fig:output1}
\end{figure}

>>>>

\chapter{Trying to Verify checkTransaction}
\label{chap:verify_check}

@@

\section{Process of Verification // TODO change}

@@

The extracted code has more than 1500 lines.
After running Stainless on it, it throws a really huge bunch of errors about what Stainless can not reason about.
And after fixing some of those errors there appear new ones as we can see in the next chapter.
This would require to change nearly everything of the extracted code.

@@

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.5]{images/bitcoin-s-pr-comment.png}
	\caption{Nice catch comment on our PR \#435 on GitHub}
	\label{fig:output1}
\end{figure}

@@
